The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-30 ms.Rmd
Make knitr create pdf and png files for each output image. The pdf output should default to using the pdfs, while the md output will use the pngs.
Clean up code a bit.

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = TRUE}
opts_chunk$set(fig.path = 'figs/', message = FALSE)

@@

```{r fengworkflow, eval = TRUE, results = 'hide', message = FALSE}
Feng_Papes <- workflow(occurrence = SpOcc('Dasypus novemcinctus',
                                          extent = c(-130, -20, -60, 60)),
                        covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                            layers = c(1:4, 6, 9, 10, 12, 15)),
                          process = Chain(Clean, # Remove rows w/ impossible, unlikely or missing lat lon.
                                          MESSMask,  # Still to be implemented. mask out areas beyond extremes in train data
                                          Background(n = 1000, bias = 200), #background w/in 200km of occurrences
                                          Crossvalidate(k = 5)),
                            model = MaxEnt,
                           output = Chain(PerformanceMeasures, PrintMap))

>>>>

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = TRUE}
opts_chunk$set(fig.path = 'figs/', message = FALSE, dev = c('pdf', 'png'))

@@

```{r fengworkflow, eval = TRUE, results = 'hide', message = FALSE}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 1000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = Chain(PerformanceMeasures, PrintMap))
